---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

#install.packages("~/Maestría/Estadística computacional/histogramR_0.1.0.tar.gz", repos = NULL)
#library(histogramR)
```

# histogramR

## Overview

histogramR is a tool based on dplyr and ggplot2 that creates classical frequency ditribution tables, histograms and frequency polygons. Also, a comparison between number of classes compute methods, as Sturges, Friedman-Diaconis and Scott, are performed. This package is part of a final work in Computational Statistics course at the Master of Applied Statistics in Universidad del Norte, Colombia.

## Installation

histogramR is stored in this github repository, thus package devtools is needed to install.

```{r eval=FALSE, include=TRUE}
install.packages(devtools)
devtools::install_github("rodianf/histogramR")

library(histogramR)
```

## Usage

### tab_freq

This function creates a classical frequency distribution table, of class tibble, with five columns.

* **variable name** Class intervals computed by selected method, default is "Sturges".

* **f** The counts or frequency of the variable in a class interval.

* **rf** The relative frequency or density.

* **cf** The cummulative frequency.

* **crf** The cummulative relative frequency.

As the return object is a tibble, functions from dplyr can be applied. To include in Rmarkdown use `knitr::kable` for better results.

#### Note

Classes with zero frequency are dropped from table. This is caused by function `group_by` from dplyr package, however a correction for this behavior will be implemented soon. See https://github.com/tidyverse/dplyr/pull/3492.

```{r}
library(MASS)

data("Melanoma")

thickness <- Melanoma$thickness

tab_freq(thickness)

tab_freq(thickness, nclass = "FD")

tab_freq(thickness) %>% 
  rename("Frequency" = f,
         "Relative frequency" = rf)

tab_freq(thickness, nclass = "scott") %>% 
  rename("Frequency" = f,
         "Relative frequency" = rf) %>% 
  knitr::kable()
```

### plot_freq

This function creates an histogram and frequency polygon or a cummulative frequency polygon. The return object is a ggplot2 plot, thus layers can be applied.

```{r}
plot_freq(thickness)

plot_freq(thickness, nclass = "FD", density = TRUE)

plot_freq(thickness, nclass = "scott", density = TRUE, cfp = TRUE) +
  theme_classic()
```

### nc_comp

This function compare the methods for calculation of the number of classes from a numerical random variable. Uses `plot_freq` function to generate plots. Generics as `print`, `summary` and `ggplot` can be used.

```{r}
nc_comp(thickness)

comparison <- nc_comp(thickness)

print(comparison)

summary(comparison)

ggplot(comparison)
```

